### 2020-02-21 Common/chapters/paper_reproduction.tex
Julien and Johan: add processing details (patient split, MRI sequences, class balancing, etc.) +  + add new challenge results + correct typos

\subsubsection{Dataset description}
\label{sec:prostatex_dataset_description}
The SPIE-AAPM-NCI PROSTATEx Challenge dataset is publicly available on the Cancer Imaging Archive. This dataset is composed of multiparametric MRIs (T2W, DWI, ADC, DCE, PD, Ktrans) for a total of 204 training patients and 208 challenge patients. Images were taken under the sagittal, transverse and coronal planes.

@@

\subsubsection{Methodology}
The methodology described in this section is the closest replication possible of the authors' data processing methodology. Most of it were reproductible in a similar way, apart from the manual lesion contouring which was performed by a qualified radiologist in the authors' case. Furthermore, the authors didn't mention any participation in the official PROSTATEx challenge. In order to get an unbiased evaluation of the performance of our model, these images were also processed as explained below in order to take part in the challenge, but were not augmented. Nevertheless, the authors created their own test set by splitting the PROSTATEx training images into a training set ($80\%$), a validation set ($10\%$) and a test set ($10\%$). They mentioned that the test set was augmented $11$ times but gave no information about the training and validation sets. Since the training set is imbalanced (3 false for 1 true), the true class was augmented more times than the false class ($60$x) in order to create balanced training and validation sets.

\subsubsection{From DICOM to NumPy arrays}
\label{sec:DICOMtoNumPy}
Before anything else, T2W, DWI and ADC grayscale images were used, which means that DCE, PD and Ktrans images were left aside. Moreover, only images showing the prostate under the transverse plane were used. The reason for this is that the tumors are much more visible under this perspective. 
The first step consisted in converting DICOM files. Algorithm \ref{alg:PROSTATEx_preprocessing} describes the steps involved in converting PROSTATEx's DICOM files to NumPy arrays. The right slices were found thanks to the two CSV files. Important information such as the patient ID, the sequence, the lesion location and the voxel spacing were used as file output names, which allows to use these files independently for the next steps (i.e. without relying on the CSV files).

@@

\subsubsection{From NumPy arrays to augmented stacked images}
\label{sec:numpyToAugmentedStacked}
This step can be split into two substeps: aligning and stacking images before augmenting them. Once full images were converted to NumPy arrays, the images related to a specific lesion of a specific patient needed to be aligned and resampled to the same resolution. In fact, T2-weighted images have a much higher resolution than the DWI and ADC images (in this dataset at least). Without this operation, a single pixel on a DWI image would have covered a lot more tissue than a pixel of the corresponding T2-image. To perform the alignment, the lesion was localized on the three sequences than to the CSV file. Then, the goal was to crop a large patch which contained the same amount of tissue on the three images. This patch had to be centered on the lesion to ease the augmentation process. So, a fixed patch size was defined for the T2-image since its resolution was the highest. Then, using the voxel spacing information, the patch size required to cover the same amount of tissue was computed for the two other sequences (DWI, ADC). Finally, the three images were cropped, resized to the same resolution and stacked. Stacking images consists in putting each single image (grayscale) into a single array, as three different channels. At this point, the pixel $i,j$ of the three channels represents the exact same tissue, which means that the lesion is at the same position and is covered by the same number of pixels on each channel. This approach increases the probability of detecting a cancer by ensuring a good visibilty for each lesion, since the latter is not necessarily as visible on the three images.

@@

Finally, the dataset was augmented in the same way as the authors. Concretely, images were rotated ($-20$ to $20^\circ$), flipped horizontally (probability of $0.5$) and slid horizontally (value $\in [-1, 0, 1]$ pixel). These techniques alone allowed to create a sufficient amount of data. Therefore, two other augmentation methods used by the authors (horizontal stretching by a factor $\in [0.9,1.1]$ and vertical sliding) were not used. Images were exported as NumPy arrays.

\subsubsection{From NumPy arrays to augmented non-stacked images}
Another way of processing and using the data was experimented. Instead of stacking the images, each image was cropped and augmented separately. At the end, each image was given as separate input to the neural network.

@@

\subsubsection{Experimental setup}
Keeping the exact same hyperparameters as the original paper lead the experiment to disappointing results. Consequently, new hyperparameters had to be found. A grid search approach driven by the AUC obtained on the test set (the one built for the experiment, not the one of the challenge) was chosen. In practical terms, this consisted in trying multiple combinations of hyperparameters and keeping the one that produced the best AUC on this test set. At the end of this process, it appeared that the best model was obtained when the data was organized in batches of 32 samples, with an initial learning rate of $1e-^{7}$, a learning rate scheduler on plateau using a factor of 100 with a patience of 2 (the learning rate is divided by 100 when the validation AUC decreases for two consecutive epochs) and a dropout rate of 0.2. Note that the model was initialized picking the best one among 200 models generated from a roulette maximizing the f1-score. This model was implemented with PyTorch using the Adam optimizer to update its weights and was trained on an Nvidia GeForce GTX Titan X graphics card during approximately 3 hours.\\

@@

As the goal of the experiment was to reproduce the experiment of the paper, a comparison between the two models is necessary. The reproducted model achieved an AUC of $0.75$ on our test set (see Figure \ref{fig:paper_reprodution_auc_on_our_test_set}) using the authors' "enhanced prediction" technique, whereas the authors achieved an AUC $\in [0.876-0.994]$ with 95\% of confidence on their test set. Consequently, the model presented in this work has a slightly smaller AUC of $[0.126-0.244]$ than the one achieved in the paper. Multiple factors can explain this difference. First, in their work, the cropping of lesions was performed by a qualified radiologist, whereas, in our case, it was automatically done using the information in the CSV files. Then, the way the test set is built can make the results vary a lot. In fact, the authors didn't provide any information about how they built their test set. It is therefore possible that the test set was chosen to maximize the performance of the model. In the current work, the test set is built randomly. Consequently, the comparison of the performance is difficult since the test set is not the same in the two works. The only way to seriously compare the two models would be to compare their performance on the official SPIE-AAPM-NCI Prostate MR classification challenge test set. The model of this section (trained with 80\% of all the data available) reached an AUC of $0.71$. Unfortunately, no information about the performance of the model of the paper is given. Knowing that the best result at the time of the challenge was an AUC of 0.87 on the challenge test set, it is highly surprising not to take part in it when claiming an AUC in the interval $[0.876-0.994]$ with 95\% of confidence... Finally, another source of difference is the number of participants in the experiment and the level of experience they have. Indeed, seven authors contributed to the paper, including one bachelors' student and six PhD with one of them working for Siemens Heathcare and one for hImagingTek Ltd. These big companies are specialized in the medical imaging and have departments dedicated to machine learning. On the opposite, this work was produced independently by two MSc students without previous experience in the medical imaging field.

\section{SPIE-AAPM-NCI Prostate MR Classification Challenge}
\label{sec:classification_challenge}
This section aims at maximizing the result on the SPIE-AAPM-NCI Prostate MR classification Challenge test set by using the entire dataset as training set, instead of using 80\% of it, as it was done in the previous section. First, the changes needed to reach this new goal are detailed, then the raw results are presented and finally the latter are interpreted.
\subsection{Training the neural network with the whole dataset}
The first part of the experiment, in which the whole dataset was split into a training (80\%), a validation (10\%) and a test set (10\%), was extremely useful to find the right hyperparameters. It also gave the opportunity to check that the model and the processing of the data worked as expected with the goal of creating a state of the art deep learning model for prostate lesions classification.\\
As a complement, this part of the experiment focuses on the challenge results in order to improve the $0.71$ in AUC achieved by the model trained with 80\% of all available data. In a general way, the more data are available the better will be the model. Consequently, the idea behind this section is to use the entire dataset as training set, discarding the validation and test sets from previous section. Apart from this new split, the data processing and the hyperparameters keep the same. The only difference in the training is about the learning rate scheduler. Indeed, since the validation set does not exist anymore, there is no possibility to use the \textit{reducelronplateau} function to prevent overfitting. However, this does not cause any problem because, thanks to the results of the previous section. In fact, is clearly visible that the model would have started to overfit at epoch 17 if no learning rate correction had been applied. Hence, it is possible to conclude that in this case the best model should also be the one around epoch 17 (or a few epochs later). In order to ensure this, the models at epoch 15, 17, 19, 20, 21, 22, 23 and 30 were evaluated on the official challenge test set. For each of these models, a csv file containing the predictions for each lesion of each patient was automatically generated and sent to the challenge.
\subsection{Results on the challenge test set}
Figure \ref{fig:results_for_all_models_challenge} shows all metrics achieved by the model on the official challenge test set during the training.
Figure \ref{fig:challenge_all_results_experiment} presents the metrics achieved by the model trained with all available data at different epochs around the epoch 20. The range of AUC values is contained in the interval [0.75-0.76].\\
Finally, figure \ref{fig:paper_reprodution_results_challenge2} shows our participation to the challenge with the model picked at epoch 20, that achieved an AUC of $0.76$.

@@

\begin{table}[]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
\hline
\rowcolor[HTML]{DAE8FC} 
\textbf{Epoch} & \textbf{15} & \textbf{17} & \textbf{19} & \textbf{20} & \textbf{21} & \textbf{22} & \textbf{23} & \textbf{30} \\ \hline
AUC            & 0.75        & 0.76        & 0.76        & 0.76        & 0.76        & 0.76        & 0.75        & 0.75        \\ \hline
\end{tabular}%
}
\caption{AUC of the model saved at different epochs on the official SPIE-AAPM-NCI Prostate MR classification test set }
\label{fig:results_for_all_models_challenge}
\end{table}

@@

\subsection{Discussion}
Figure \ref{fig:challenge_all_results_experiment} illustrates once again the correct behaviour of the model during the training. All metrics reach their point of convergence, the curves do not oscillate much and the loss curve is continually decreasing, which is a good learning indicator. In comparison to the the first part of the experiment, it is clearly visible that all metrics have an higher best value. This is due to the absence of learning rate scheduler during the training. As a result, from a certain epoch, all features learned by the model are not transposable to unseen data and the latter overfits the data. To determine this point, multiple models around the epoch 20 were evaluated on the challenge test set (see Figure \ref{fig:results_for_all_models_challenge}). It is noticeable that the model before epoch 15 did not reach its best performance and after epoch 23 was overfitting. All models between these two epochs achieve an AUC of $0.76$ on the challenge.\\
In comparison to the model of the previous section trained on 80\% of all available data that achieved an AUC of $0.71$ on the challenge, this new one improves the performance by 0.05. This is a clear indication that the more data is available the better is the model.\\
Finally, regarding the overall leaderboard of all challenge participants at the time of the challenge, the model is well ranked. Indeed, with respect to the 71 submissions to the PROSTATEx challenge (see Figure \ref{fig:challenge_all_results}), the AUC of $0.76$ achieved in this work would place the model in 15th position approximately.

>>>>

\subsubsection{Dataset description}
\label{sec:prostatex_dataset_description}
The SPIE-AAPM-NCI PROSTATEx Challenge dataset is publicly available on the Cancer Imaging Archive website. This dataset is composed of multiparametric MRIs for a total of 204 training patients and 208 challenge patients. Images were taken under the sagittal, transverse and coronal planes. These MRIs are multiparametric because the same exam was performed using different radiological settings called "sequences". Each sequence allows to see human tissues in a different way on the resulting images. The sequences available within the scope of PROSTATEx are T2 weighted images (T2W), Diffusion weighted images (DWI), Apparent diffusion coefficient (ADC), Dynamic contrast enhanced (DCE), PD (Proton Density) and K-trans.

@@

\subsubsection{Methodology}
The methodology described in this section is the closest replication possible of the authors' data processing methodology. Most of it were reproductible in a similar way, apart from the manual lesion contouring which was performed by a qualified radiologist in the authors' case. Furthermore, the authors did not mention any participation in the official PROSTATEx challenge. In order to get an unbiased evaluation of the performance of our model, these images were also processed as explained below in order to take part in the challenge, but were not augmented. Nevertheless, the authors created their own test set by splitting the PROSTATEx training images into a training set ($80\%$), a validation set ($10\%$) and a test set ($10\%$). They mentioned that the test set was augmented $11$ times but gave no information about the training and validation sets. Since the training set is imbalanced (3 false for 1 true), the true class was augmented more times than the false class ($60$x) in order to create balanced training and validation sets.

\subsubsection{From DICOM to NumPy arrays}
\label{sec:DICOMtoNumPy}
Before anything else, T2W, DWI and ADC grayscale images were used, which means that DCE, PD and Ktrans images were left aside. Furthermore, DWI images regroup various parameters which create different subcategories. One of them is the so-called "b-value" which is "a factor that reflects the strength and timing of the gradients used to generate diffusion-weighted images. The higher the b-value, the stronger the diffusion effects" \cite{49}. The authors tested three different b-value configurations. This led to the conclusion that using DWI images with the highest b-value increased the performance of the model. For that matter, DWI images with the highest b-value only were used. \\
Moreover, only images showing the prostate under the transverse plane were used. The reason for this is that the tumors are much more visible under this perspective. 
The first step consisted in converting DICOM files. Algorithm \ref{alg:PROSTATEx_preprocessing} describes the steps involved in converting PROSTATEx's DICOM files to NumPy arrays. The right slices were found thanks to the two CSV files. Important information such as the patient ID, the sequence, the lesion location and the voxel spacing were used as file output names, which allows to use these files independently for the next steps (i.e. without relying on the CSV files).

@@

\subsubsection{From NumPy arrays to augmented stacked images}
\label{sec:numpyToAugmentedStacked}
This step can be split into two substeps: aligning and stacking images before augmenting them and splitting them across a training set, a validation set and a test set.

Once full images were converted to NumPy arrays, the images related to a specific lesion of a specific patient needed to be aligned and resampled to the same resolution. In fact, T2-weighted images have a much higher resolution than the DWI and ADC images (in this dataset at least). Without this operation, a single pixel on a DWI image would have covered a lot more tissue than a pixel of the corresponding T2 image. To perform the alignment, the lesion was localized on the three sequences than to the CSV file. Then, the goal was to crop a large patch which contained the same amount of tissue on the three images. This patch had to be centered on the lesion to ease the augmentation process. So, a fixed patch size was defined for the T2 image since its resolution was the highest. Then, using the voxel spacing information, the patch size required to cover the same amount of tissue was computed for the two other sequences (DWI, ADC). Finally, the three images were cropped, resized to the same resolution and stacked. Stacking images consists in putting each single image (grayscale) into a single array, as three different channels. At this point, the pixel $i,j$ of the three channels represents the exact same tissue, which means that the lesion is at the same position and is covered by the same number of pixels on each channel. This approach increases the probability of detecting a cancer by ensuring a good visibilty for each lesion, since the latter is not necessarily as visible on the three images.

@@

Then, the dataset was augmented in the same way as the authors. Concretely, images were rotated ($-20$ to $20^\circ$), flipped horizontally (probability of $0.5$) and slid horizontally (value $\in [-1, 0, 1]$ pixel). These techniques alone allowed to create a large enough amount of data. Therefore, two other augmentation methods used by the authors (horizontal stretching by a factor $\in [0.9,1.1]$ and vertical sliding) were not used.\\
On the other hand, authors did not mention how they managed class imbalance. It seems like the manual lesion contouring performed by the qualified radiologist led to a natural class balance. However, the unmodified dataset has a ratio of 3 negative images for 1 positive. To solve this problem, multiple approaches were implemented. The first one made use of undersampling which consists in taking N elements of each class, where N is the size of the class whose number of elements is the smallest. As the size of the dataset is relatively small, taking a subset of it was not a good idea and led to a clear lack of data. The second solution solved the problem by using different augmentation factors. In fact, one of the script options sets the augmentation factor for the class whose number of elements is the largest. Then, according to this factor, the algorithm computes the augmentation factor for the other class in order to balance the final datasets. For example, if the dataset follows the above-mentioned 3 negatives for 1 positive ratio, and if the script option augmentation factor is set to 50, each image belonging to the negative class is going to be augmented 50 times and each image belonging to the positive class 150 times. At the end, the resulting dataset is balanced and makes use of all images.

Finally, the data was split into three subsets (training ($80$\%), validation ($10$\%) and test ($10$\%)) and was exported as NumPy arrays. The percentages represent a percentage of patients. In fact, each subset contains respectively 80\%, 10\% and 10\% of the 204 patients, i.e. $\lfloor 0.8 * 204 \rfloor = 163$ training patients, $\lfloor 0.1 * 204 \rfloor = 20$ test patients and $204 - 163 - 20 = 21$ validation patients. This approach does not take the number of images into account (a patient may have multiple lesions for example) but guarantees that every lesion is exclusive to a specific subset. In other words, it is impossible to find a slighty different version of the same lesion (resulting from the data augmentation) in the training set and in the validation set for example. This would be problematic since the validation set, as well as the test set, need to contain unseen data to be able to evaluate the generalization ability of the model in an unbiased way.

\subsubsection{From NumPy arrays to augmented non-stacked images}
Another way of processing and using the data was tested. Instead of stacking the images of various sequences coming from the same exam, each image was treated independently. In other words, each of them was resized as explained previously, then cropped, augmented and exported separately. At the end, each image was fed as separate input to the neural network.

This way of proceeding gave awful results. The main reason is that images from different sequences show the same tissue in an almost opposite way. The most striking difference to the human eye is the colors. Tumors are usually white on DWI images and black on ADC images. Moreover, they are not always as visible on the images of the various sequences. Therefore, finding similar features on all sequences was extremely difficult. Stacking the three sequences solves this problem. In this case, the first 4225 input neurons (4225 input neurons for a $65$x$65$px image) are dedicated to T2 images, the next 4225 neurons to DWI images and the last 4225 neurons to ADC images.

@@

\subsubsection{Experimental setup}
Keeping the exact same hyperparameters as the original paper led the experiment to disappointing results. Consequently, new hyperparameters had to be found. A grid search approach driven by the AUC obtained on the test set (the one built for the experiment, not the one of the challenge) was chosen. In practical terms, this consisted in trying multiple combinations of hyperparameters and keeping the one that produced the best AUC on this test set. At the end of this process, it appeared that the best model was obtained when the data was organized in batches of 32 samples, with an initial learning rate of $1e-^{7}$, a learning rate scheduler on plateau using a factor of 100 with a patience of 2 (the learning rate is divided by 100 when the validation AUC decreases for two consecutive epochs) and a dropout rate of 0.2. Note that the model was initialized picking the best one among 200 models generated from a roulette maximizing the f1-score. This model was implemented with PyTorch using the Adam optimizer to update its weights and was trained on an Nvidia GeForce GTX Titan X graphics card during approximately 3 hours.\\

@@

As the goal of the experiment was to reproduce the experiment of the paper, a comparison between the two models is necessary. The reproducted model achieved an AUC of $0.75$ on our test set (see Figure \ref{fig:paper_reprodution_auc_on_our_test_set}) using the authors' "enhanced prediction" technique, whereas the authors achieved an AUC $\in [0.876-0.994]$ with 95\% of confidence on their test set. Consequently, the model presented in this work has a slightly smaller AUC of $[0.126-0.244]$ than the one achieved in the paper. Multiple factors can explain this difference. First, in their work, the cropping of lesions was performed by a qualified radiologist, whereas, in our case, it was automatically done using the information in the CSV files. Then, the way the test set is built can make the results vary a lot. In fact, the authors didn't provide any information about how they built their test set. It is therefore possible that the test set was chosen to maximize the performance of the model. In the current work, the test set is built randomly. Consequently, the comparison of the performance is difficult since the test set is not the same in the two works. The only way to seriously compare the two models would be to compare their performance on the official SPIE-AAPM-NCI Prostate MR classification challenge test set. The model of this section (trained with 80\% of all the data available) reached an AUC of $0.71$. Unfortunately, no information about the performance of the model of the paper is given. Knowing that the best result at the time of the challenge was an AUC of $0.87$ on the challenge test set, it is highly surprising not to take part in it when claiming an AUC in the interval $[0.876-0.994]$ with 95\% of confidence... Finally, another source of difference is the number of participants in the experiment and the level of experience they have. Indeed, seven authors contributed to the paper, including one bachelors' student and six PhD with one of them working for Siemens Heathcare and one for hImagingTek Ltd. These big companies are specialized in the medical imaging and have departments dedicated to machine learning. On the opposite, this work was produced independently by two MSc students without previous experience in the medical imaging field.

\section{SPIE-AAPM-NCI Prostate MR Classification Challenge}
\label{sec:classification_challenge}
This section aims at maximizing the result on the SPIE-AAPM-NCI Prostate MR classification Challenge test set by using the entire dataset as training set, instead of using 80\% of it, as it was done in the previous section. First, the changes needed to reach this new goal are detailed, then the raw results are presented and the latter are finally interpreted.

\subsection{Training the neural network with the whole dataset}
The first part of the experiment, in which the whole dataset was split into a training (80\%), a validation (10\%) and a test set (10\%), was extremely useful to find the right hyperparameters. It also gave the opportunity to check that the model and the processing of the data worked as expected with the goal of creating a state-of-the-art deep learning model for prostate lesions classification.\\
As a complement, this part of the experiment focuses on the challenge results in order to improve the $0.71$ in AUC achieved by the model trained with 80\% of all available data. In a general way, the more available data there is, the better the model performs. Consequently, the idea behind this section is to use the entire dataset as training set, discarding the validation and test sets from previous section. Apart from this new split, the data processing and the hyperparameters stay the same. The only difference in the training is about the learning rate scheduler. Since the validation set does not exist anymore, there is no possibility to use the \textit{reducelronplateau} function to prevent overfitting. However, this does not cause any problem thanks to the results of the previous section. In fact, it is clearly visible that the model would have started to overfit at epoch 17 if no learning rate correction had been applied. Hence, it is possible to conclude that, in this case, the best model should also be the one around epoch 17 (or a few epochs later). In order to ensure this, the models at epochs 15, 16, 17, 18, 19, 20, 21, 22, 23 and 30 were evaluated on the official challenge test set. For each of these models, a CSV file containing the predictions for each lesion of each patient was automatically generated and submitted to the challenge.

\subsection{Results on the challenge test set}
Table \ref{fig:results_for_all_models_challenge} shows the AUC values achieved by the model on the official challenge test set. The range of values is contained in the interval $[0.75-0.76]$. Each model was tested in order to see if a slight peak of $0.01$ could be found from one epoch to the other.\\ 
Figure \ref{fig:challenge_all_results_experiment} presents the metric values the model reached while training on the whole dataset. The models whose results are reported in Table \ref{fig:results_for_all_models_challenge} were picked from this training.\\
Finally, Figure \ref{fig:paper_reprodution_results_challenge2} shows our participation to the challenge with the model picked at epoch 20, which achieved an AUC of $0.76$.

@@

\begin{table}[]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|}
\hline
\rowcolor[HTML]{DAE8FC} 
\textbf{Epoch} & \textbf{15} & \textbf{16} & \textbf{17} & \textbf{18} & \textbf{19} & \textbf{20} & \textbf{21} & \textbf{22} & \textbf{23} & \textbf{30} \\ \hline
AUC            & 0.75        & 0.75        & 0.76        & 0.76        & 0.76        & 0.76        & 0.76        & 0.76        & 0.75        & 0.75        \\ \hline
\end{tabular}%
}
\caption{AUC of the model saved at different epochs on the official SPIE-AAPM-NCI Prostate MR classification test set }
\label{fig:results_for_all_models_challenge}
\end{table}

@@

\subsection{Discussion}
Figure \ref{fig:challenge_all_results_experiment} illustrates once again the correct behavior of the model during the training. All metrics reach their point of convergence at some point, the curves do not oscillate much and the loss curve is continually decreasing, which is a good learning indicator. In comparison to the the first part of the experiment, it is clearly visible that the metrics have an higher best value. This is due to the absence of learning rate scheduler during the training. As a result, from a certain epoch onwards, features learned by the model are not transposable to unseen data anymore and the latter overfits the data. To determine this point, multiple models around the epoch 20 were evaluated on the challenge test set (see Figure \ref{fig:results_for_all_models_challenge}). It is noticeable that the model did not reach its best performance before epoch 15 and that it started overfitting after epoch 23. Every model between these two epochs achieved an AUC of $0.76$ on the challenge, which seems to be the optimum value with this data and this configuration.\\
In comparison to the model of the previous section trained on 80\% of the available data, this new one improves the performance by $0.05$ (AUC of $0.76$ vs $0.71$). This is a clear indication that the more data there is, the better the model performs.\\
Finally, regarding the overall leaderboard of all challenge participants at the time of the challenge, the model would have been well ranked. Indeed, according to the 71 submissions to the PROSTATEx challenge (see Figure \ref{fig:challenge_all_results}), the AUC of $0.76$ achieved in this work would place the model at the 15$^{th}$ position overall.

### 2020-02-21 Common/chapters/transfer_learning.tex
Julien and Johan: add processing details (patient split, MRI sequences, class balancing, etc.) +  + add new challenge results + correct typos

\section{Data processing}
\subsection{PROSTATEx}
\label{sec:PROSTATEx}
As the other datasets used in this work don't contain multi-sequence exams (single-sequence MRIs and CT scans), it was required to extract single channel images from the PROSTATEx dataset. DWI images were selected because lesions are white on this sequence, as well as on CT scans. Hence, choosing DWI images ensured a consistent representation of tumors from one dataset to the other, which helps the cancer detection.

@@

Ideally, transfer learning should rely on multi-sequence MRIs only. In fact, the extra information provided by different sequences increases the performance a lot. However, publicly available datasets either don't contain the clinical significance of the samples or were purely made for segmentation purposes (where labels are also images).

@@

At the end of the transfer learning pipeline, a graph was generated for each metric. These curves show the evolution of the latter across the entire process, which allows to determine the impact of each non-target dataset on the target task. If a metric is increasing, the features learned thanks to the corresponding dataset are useful for the target one. Figure \ref{fig:global_performance_example} shows an example of this graph for the AUC.\\
As expected, the curve is flat during the frozen parts. Since the same decision maker is attached to frozen layers (which remain the same by definition), the values of the metrics don't change at all.

>>>>

\section{Data processing}
\subsection{PROSTATEx}
\label{sec:PROSTATEx}
As the other datasets used in this work do not contain multi-sequence exams (single-sequence MRIs and CT scans), it was required to extract single channel images from the PROSTATEx dataset. DWI images were selected because lesions are white on this sequence, as well as on CT scans. Hence, choosing DWI images ensured a consistent representation of tumors from one dataset to the other, which helps the cancer detection.

@@

Ideally, transfer learning should rely on multi-sequence MRIs only. In fact, the extra information provided by different sequences increases the performance a lot. However, publicly available datasets either do not contain the clinical significance of the samples or were purely made for segmentation purposes (where labels are also images).

@@

At the end of the transfer learning pipeline, a graph was generated for each metric. These curves show the evolution of the latter across the entire process, which allows to determine the impact of each non-target dataset on the target task. If a metric is increasing, the features learned thanks to the corresponding dataset are useful for the target one. Figure \ref{fig:global_performance_example} shows an example of this graph for the AUC.\\
As expected, the curve is flat during the frozen parts. Since the same decision maker is attached to frozen layers (which remain the same by definition), the values of the metrics do not change at all.
